An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-12-02 paper/4.xpg.tex
change fail to undefined

    \noindent $\tabs{2} \pg{Skip \ h}{s}{v} \overset{1}{=} (\sif{h \ s = v}{s}{\text{fail}}, h \ s) \\
        \tab \qtab \overset{2}{=} \sif{h \ s = v}{(s, h \ s)}{\text{fail}} \\
        \tab \qtab \overset{3}{=} \sif{h \ s = v}{(s, v)}{\text{fail}}$

The first equality is simply based on the definitions of $pg$, $\putbxinline{Skip \ h}$ and $\getbxinline{Skip \ h}$. The second one tuples two results of $put$ and $get$ in the body of the if-expression. This is a trick since in some cases, the result of $pg$ may be fail although there is no fail when evaluating $\getbxinline{Skip \ h}$. The last equality is relatively oblivious.

@@

    \noindent $\cpg{Skip \ h}{ks}{kv}{s}{v} = \text{ if } h \ s = v \text{ then } (ks, kv, s, v) \text{ else fail}$

@@

    \noindent $\kpg{Skip \ h}{ks}{kv}{ks'}{kv'}{s}{v} =\\
        \tab s \Leftarrow ks' \ s; \quad v \Leftarrow kv' \ v; \quad ks' \Leftarrow id; \quad kv' \Leftarrow id;\\
        \tab \text{if} \ h \ s = v \ \text{then} \ (ks, kv, ks', kv', s, v) \ \text{else fail}$

>>>>

    \noindent $\tabs{2} \pg{Skip \ h}{s}{v} \overset{1}{=} (\sif{h \ s = v}{s}{\text{undefined}}, h \ s) \\
        \tab \qtab \overset{2}{=} \sif{h \ s = v}{(s, h \ s)}{\text{undefined}} \\
        \tab \qtab \overset{3}{=} \sif{h \ s = v}{(s, v)}{\text{undefined}}$

The first equality is simply based on the definitions of $pg$, $\putbxinline{Skip \ h}$ and $\getbxinline{Skip \ h}$. The second one tuples two results of $put$ and $get$ in the body of the if-expression. This is a trick since in some cases, the result of $pg$ may be undefined although there is no undefined when evaluating $\getbxinline{Skip \ h}$. The last equality is relatively oblivious.

@@

    \noindent $\cpg{Skip \ h}{ks}{kv}{s}{v} = \text{ if } h \ s = v \text{ then } (ks, kv, s, v) \text{ else undefined}$

@@

    \noindent $\kpg{Skip \ h}{ks}{kv}{ks'}{kv'}{s}{v} =\\
        \tab s \Leftarrow ks' \ s; \quad v \Leftarrow kv' \ v; \quad ks' \Leftarrow id; \quad kv' \Leftarrow id;\\
        \tab \text{if} \ h \ s = v \ \text{then} \ (ks, kv, ks', kv', s, v) \ \text{else undefined}$
